A Mechanical Formalization of Higher-Ranked Polymorphic Type Inference

### 2019-05-29 sections/Overview.tex
further updates

\jimmy{Mention the implicit freshness conditions in the premises throughout the text}
Please note that when we introduce a new binder in the premise, we implicitly pick a fresh one.
This applies to rules such as $\mathtt{wf_d\forall}$, $\mathtt{wf_dabs}$, $\mathtt{{\le}\forall R}$,
throughout the whole text.
For algorithmic rules in Figure~\ref{fig:alg}, the right-hand side $\Gm'$
is actually the premise if re-written in a big-step style.
\bruno{Comment about big-step seems out of place. Should come later,
  when we actually talk about the algorithm.}

>>>>

\jimmy{Mention the implicit freshness conditions in the premises}
Please note that when we introduce a new binder in the premise, we implicitly pick a fresh one.
This applies to rules such as $\mathtt{wf_d\forall}$, $\mathtt{wf_dabs}$, $\mathtt{{\le}\forall R}$,
throughout the whole text.

### 2019-05-29 sections/algorithm.tex
Fig 4 spacing and title
further updates

\centering \framebox{$\Gm \vdash A$}
\begin{gather*}
\inferrule*[right=$\mathtt{wf\_ unit}$]
    {~}{\Gm\vdash 1}
\qquad
\inferrule*[right=$\mathtt{wf\_ var}$]
    {a\in\Gm}{\Gm\vdash a}
\qquad
\inferrule*[right=$\mathtt{wf\_ exvar}$]
    {\al\in\Gm}{\Gm\vdash \al}
\qquad
\inferrule*[right=$\mathtt{wf\_{\to}}$]
    {\Gm\vdash A\quad \Gm\vdash B}
    {\Gm\vdash A\to B}
\qquad
\inferrule*[right=$\mathtt{wf\_\forall}$]
    {\Gm, a\vdash A}
    {\Gm\vdash \forall a. A}
\end{gather*}

\centering \framebox{$\Gm \vdash e$}
\begin{gather*}
\inferrule*[right=$\mathtt{wf\_ tmvar}$]
    {x:A\in\Gm}{\Gm\vdash x}
\qquad
\inferrule*[right=$\mathtt{wf\_ tmunit}$]
    {~}{\Gm\vdash ()}
\qquad
\inferrule*[right=$\mathtt{wf\_ abs}$]
    {\Gm,x:A\vdash e}
    {\Gm\vdash \lam e}
\\
\inferrule*[right=$\mathtt{wf\_ app}$]
    {\Gm\vdash e_1 \quad \Gm\vdash e_2}
    {\Gm\vdash e_1~e_2}
\qquad
\inferrule*[right=$\mathtt{wf\_ anno}$]
    {\Gm\vdash A \quad \Gm\vdash e}
    {\Gm\vdash (e:A)}
\end{gather*}

@@

@@

>>>>

\centering \framebox{$\Gm \vdash A$} Well-formed algorithmic type
\begin{gather*}
\inferrule*[right=$\mathtt{wf\_ unit}$]
    {~}{\Gm\vdash 1}
\quad
\inferrule*[right=$\mathtt{wf\_ var}$]
    {a\in\Gm}{\Gm\vdash a}
\quad
\inferrule*[right=$\mathtt{wf\_ exvar}$]
    {\al\in\Gm}{\Gm\vdash \al}
\quad
\inferrule*[right=$\mathtt{wf\_{\to}}$]
    {\Gm\vdash A\quad \Gm\vdash B}
    {\Gm\vdash A\to B}
\quad
\inferrule*[right=$\mathtt{wf\_\forall}$]
    {\Gm, a\vdash A}
    {\Gm\vdash \forall a. A}
\end{gather*}

\centering \framebox{$\Gm \vdash e$} Well-formed algorithmic expression
\begin{gather*}
\inferrule*[right=$\mathtt{wf\_ tmvar}$]
    {x:A\in\Gm}{\Gm\vdash x}
\qquad
\inferrule*[right=$\mathtt{wf\_ tmunit}$]
    {~}{\Gm\vdash ()}
\qquad
\inferrule*[right=$\mathtt{wf\_ abs}$]
    {\Gm,x:A\vdash e}
    {\Gm\vdash \lam e}
\\
\inferrule*[right=$\mathtt{wf\_ app}$]
    {\Gm\vdash e_1 \quad \Gm\vdash e_2}
    {\Gm\vdash e_1~e_2}
\qquad
\inferrule*[right=$\mathtt{wf\_ anno}$]
    {\Gm\vdash A \quad \Gm\vdash e}
    {\Gm\vdash (e:A)}
\end{gather*}

@@

\jimmy{The implicit freshness conditions for algorithmic system}

Please note that when a new binder is introduced in the right-hand side worklist $\Gm'$,
we implicitly pick a fresh one,
since the right-hand side can be seen as the premise of the reduction.

@@

One may notice that the subtyping relation for simple types is just equivalence,
which is true according to the declarative system.
The DK's system works in a similar way.
